Appendix to "Fast approximate Bayesian inference of HIV indicators using principal components analysis adaptive Gauss-Hermite quadrature

### 2023-06-22 src/docs_paper/appendix.Rmd
Mostly working on MLGH presentation, some other writing
Lots of Seth fixes, change paper name, change repo name #55

---
title: Appendix to "Fast approximate Bayesian inference of HIV indicators using the Naomi small-area estimation model"
author:
  - Adam Howes^[Department of Mathematics, Imperial College London]
  - Alex Stringer^[Department of Statistics and Actuarial Science, University of Waterloo]
  - Seth R. Flaxman^[Department of Computer Science, Oxford University]
  - Jeffrey W. Eaton^[Harvard T.H. Chan School of Public Health, Harvard University]
output:
  pdf_document:
    toc: yes
    number_sections: yes
    keep_tex: yes
    includes:
      in_header: preamble.tex
bibliography: citations.bib
cls: imsart.cls
---

@@

<!-- Had previously been getting a figure of 491 somewhere -- which is 51 + 14n + 24. Something going on there? -->

>>>>

---
title: Appendix to "Fast approximate Bayesian inference of HIV indicators using principal components analysis adaptive Gauss-Hermite quadrature"
author:
  - Adam Howes^[Department of Mathematics, Imperial College London]
  - Alex Stringer^[Department of Statistics and Actuarial Science, University of Waterloo]
  - Seth R. Flaxman^[Department of Computer Science, Oxford University]
  - Jeffrey W. Eaton^[Harvard T.H. Chan School of Public Health, Harvard University]
output:
  pdf_document:
    toc: yes
    number_sections: yes
    keep_tex: yes
    includes:
      in_header: preamble.tex
bibliography: citations.bib
cls: imsart.cls
---

@@

<!-- 51 + 13n + 467 is the value I get from the code. 467 + 24 = 491 total -->
<!-- Need to check the discrepency -->
